---
title: "apoptotic_example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{apoptotic_example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.height = 5
)
```

```{r setup}
library(intactr)
```

## Calculate genetic interaction scores for an apoptotic library screened with Cas12a

The data: 
* 22 genes involoved in apoptosis
* 10 guides per gene
* 20 olfactory receptor controls
* columns gene1, guide1, guide2, control1, control2

```{r}
knitr::kable(head(apop_combo_lfcs))
```

We calculate score for combinations by taking the residual from a line fit to each guide. For example, here are the residual plots for all guides tragetting BCL2L1 and MCL1

```{r}
plot_combo_residuals('BCL2L1', 'MCL1', apop_combo_lfcs, 10)
```

```{r}
combo_scores <- calculate_anchor_residuals(apop_combo_lfcs, 10)
knitr::kable(head(combo_scores))
```

```{r}
plot_score_heatmap(combo_scores, 'combo_z_score')
```

Our strongest hits include well known interactors as well as novel hits. 

```{r}
plot_hit_network(combo_scores, 'combo_z_score', 5)
```

One particularly interesting novel hit is the one between *WSB2* and *MARCH5*

```{r}
plot_combo('WSB2', 'MARCH5', apop_combo_lfcs)
```



